Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds

### 2020-08-22 Sexual Selection and Speciation.Rmd
new figure with mating system

```{r setup, message=FALSE, warning=FALSE}
library(ggplot2)
library(pander)
library(knitr)
library(tidyr)
library(mgcv)
library(diversitree)
library(repmis)
library(lme4)
library(ape)
library(geiger)
library(grid)
library(svglite)
library(gridExtra)
library(nlme)
library(phytools)
library(brms)
library(ggridges)
library(caper)
library(purrr)
library(reshape2)
library(ggExtra)
library(grid)
library(dplyr)
library(BAMMtools)
library(gridExtra)
library(car)
library(coda)
library(MuMIn)
library(parallel)
library(HDInterval)
library(phangorn)
library(kableExtra)
library(RColorBrewer)
library(tibble)
library(stargazer)
library(ggraph)
library(ggiraphExtra)
library(stringr)
library(Cairo)
library(gdtools)
library(data.table)
library(bindrcpp)
#devtools::install_github("Ax3man/phylopath")
#devtools::install_github("thomasp85/patchwork")
#devtools::install_github('VPetukhov/ggrastr')
library(ggrastr)
library(patchwork)
library(phylopath)
library(sjPlot)
library(sjmisc)
if(!requireNamespace("BiocManager", quietly = TRUE)){
    install.packages("BiocManager")
  }
#BiocManager::install(c("EBImage", "ggtree"))
library("EBImage") # for images
library("ggtree")
library("ggnewscale")
source("bamm_extinction/functions/check_and_fix_ultrametric.R")
source("functions/essim.R")
source("functions/diversification_rate_calculation.R")
source("functions/Vdodge_function.R")
source('functions/symmetrise_scale.R')
source('functions/Correlation_matrix.R')
source('functions/gheatmap2.R') #Gets rid of spaces between tiles
knitr::opts_chunk$set(cache=TRUE)
```

@@

>>>>

```{r setup, message=FALSE, warning=FALSE}
library(ggplot2)
library(pander)
library(knitr)
library(tidyr)
library(mgcv)
library(diversitree)
library(repmis)
library(lme4)
library(ape)
library(geiger)
library(grid)
library(svglite)
library(gridExtra)
library(nlme)
library(phytools)
library(brms)
library(ggridges)
library(caper)
library(purrr)
library(reshape2)
library(ggExtra)
library(grid)
library(dplyr)
library(BAMMtools)
library(gridExtra)
library(car)
library(coda)
library(MuMIn)
library(parallel)
library(HDInterval)
library(phangorn)
library(kableExtra)
library(RColorBrewer)
library(tibble)
library(stargazer)
library(ggraph)
library(ggiraphExtra)
library(stringr)
library(Cairo)
library(gdtools)
library(data.table)
library(bindrcpp)
library(captioner)
#devtools::install_github("Ax3man/phylopath")
#devtools::install_github("thomasp85/patchwork")
#devtools::install_github('VPetukhov/ggrastr')
library(ggrastr)
library(patchwork)
library(phylopath)
library(sjPlot)
library(sjmisc)
library(egg)
if(!requireNamespace("BiocManager", quietly = TRUE)){
    install.packages("BiocManager")
  }
#BiocManager::install(c("EBImage", "ggtree"))
library("EBImage") # for images
library("ggtree")
library("ggnewscale")
source("bamm_extinction/functions/check_and_fix_ultrametric.R")
source("functions/essim.R")
source("functions/diversification_rate_calculation.R")
source("functions/Vdodge_function.R")
source('functions/symmetrise_scale.R')
source('functions/Correlation_matrix.R')
source('functions/gheatmap2.R') #Gets rid of spaces between tiles
knitr::opts_chunk$set(cache=TRUE)

supp_figs <- captioner::captioner(prefix = "Figure S", auto_space = F)

counter_fig <- function() {
  if(!exists('counter_iteration')) {
    counter_iteration <<- 1L
  } else {
    counter_iteration <<- counter_iteration + 1L
  }
  print(counter_iteration)
}
```

@@

<!-- ## Sexual selection components effects on speciation   -->

```{r individual_components, fig.height = 8, fig.width = 7, warning = F, message = F, include=FALSE, echo = FALSE, eval = FALSE}
#### Read files with summary results: Additional analyses were conducted seperate from this RMarkdown; Contact authors for information ----

nd.wing <- readRDS('data/Subset.ND.pgls.summaryA.rds')[1:300]
nd.mating <- readRDS('data/Subset.ND.pgls.summary_mating.rds')[1:300]
nd.paternal <- readRDS('data/Subset.ND.pgls.summary_paternal.rds')
dr.wing <- readRDS('data/Subset.DR.pgls.summary_sswing.rds')
dr.mating <- readRDS('data/Subset.DR.pgls.summary_mating.rds')
dr.paternal <- readRDS('data/Subset.DR.pgls.summary_paternal.rds')
b.wing <- readRDS('data/Subset.Lambda.pgls.summaryB.rds')
b.mating <- readRDS('data/Subset.Lambda.pgls.summary_mating.rds')
b.paternal <- readRDS('data/Subset.Lambda.pgls.summary_paternal.rds')

# Subset.ND.pgls.summary <- dplyr::bind_rows(b.wing, b.paternal) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
# 
# Subset.ND.pgls.summary <- dplyr::filter(Subset.ND.pgls.summary, Parameter %in% c('abs(SSD_wing)', 'as.factor(paternal_care)1'))

#HPDinterval(as.mcmc(Subset.ND.pgls.summary$Estimate), prob=0.95)

#### Graph for paternal care ####

Subset.ND.pgls.summary=nd.paternal
Subset.ND.pgls.summary <- bind_rows(Subset.ND.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
Subset.ND.pgls.summary = filter(Subset.ND.pgls.summary,Parameter == 'as.factor(paternal_care)1')
HPD_Interval_ND_PC <- HPDinterval(as.mcmc(Subset.ND.pgls.summary$Estimate), prob=0.95) %>% as.data.frame %>% dplyr::mutate(Parameter = 'as.factor(paternal_care)1')

Subset.ND.plot <-Subset.ND.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6), fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1, colour="black", fill="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-0.25, 0.25)) +
  annotate("text", x=-0.22, y=1.5, label= expression(lambda[ND])) + xlab(" ") + ylab(" ") +
  geom_errorbarh(data = HPD_Interval_ND_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  theme(panel.grid.major.y = element_blank())
  # geom_text(aes(y=Parameter, x = Estimate, label=""), position = position_nudge(y = -0.8), inherit.aes = F)

Subset.DR.pgls.summary=dr.paternal
Subset.DR.pgls.summary <- bind_rows(Subset.DR.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
Subset.DR.pgls.summary = filter(Subset.DR.pgls.summary,Parameter == 'as.factor(paternal_care)1')
HPD_Interval_DR_PC <- HPDinterval(as.mcmc(Subset.DR.pgls.summary$Estimate), prob=0.95) %>% 
  as.data.frame %>% 
  dplyr::mutate(Parameter = 'as.factor(paternal_care)1')

Subset.DR.plot <-Subset.DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-0.25, 0.25))+
  annotate("text", x=-0.22, y=1.5, label= expression(lambda[DR])) + xlab(" ") + ylab(" ") + 
    geom_errorbarh(data = HPD_Interval_DR_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  theme(panel.grid.major.y = element_blank())

Subset.B.pgls.summary=b.paternal
Subset.B.pgls.summary <- bind_rows(Subset.B.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
Subset.B.pgls.summary = filter(Subset.B.pgls.summary,Parameter == 'as.factor(paternal_care)1')
HPD_Interval_B_PC <- HPDinterval(as.mcmc(Subset.B.pgls.summary$Estimate), prob=0.95) %>% 
  as.data.frame %>% 
  dplyr::mutate(Parameter = 'as.factor(paternal_care)1')

Subset.B.plot <-Subset.B.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-0.25, 0.25)) +
  annotate("text", x=-0.20, y=1.5, label= expression(lambda[BAMM])) +
  geom_errorbarh(data = HPD_Interval_B_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  xlab("Estimate (paternal care)") + ylab("") +
  theme(panel.grid.major.y = element_blank())

#Paternal_graph=ggarrange(Subset.ND.plot,Subset.DR.plot,Subset.B.plot, ncol=1)

#### Graph for sexual dimorphism ####

Subset.ND.pgls.summary=nd.wing
Subset.ND.pgls.summary <- bind_rows(Subset.ND.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
Subset.ND.pgls.summary = filter(Subset.ND.pgls.summary,Parameter == 'abs(SSD_wing)')
HPD_Interval_ND_W <- HPDinterval(as.mcmc(Subset.ND.pgls.summary$Estimate), prob=0.95) %>% as.data.frame %>% dplyr::mutate(Parameter = 'abs(SSD_wing)')

Subset.ND.plot2 <-Subset.ND.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6), fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1, colour="black", fill="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-2.5, 4)) +
  xlab(" ") + ylab(" ") +
    geom_errorbarh(data = HPD_Interval_ND_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

Subset.DR.pgls.summary=dr.wing
Subset.DR.pgls.summary <- bind_rows(Subset.DR.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
Subset.DR.pgls.summary = filter(Subset.DR.pgls.summary,Parameter == 'abs(SSD_wing)')
HPD_Interval_DR_W <- HPDinterval(as.mcmc(Subset.DR.pgls.summary$Estimate), prob=0.95) %>% as.data.frame %>% dplyr::mutate(Parameter = 'abs(SSD_wing)')

Subset.DR.plot2 <-Subset.DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-2.5, 4)) +
  xlab(" ") + ylab(" ") +
  geom_errorbarh(data = HPD_Interval_DR_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

Subset.B.pgls.summary=b.wing
Subset.B.pgls.summary <- bind_rows(Subset.B.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))
Subset.B.pgls.summary = filter(Subset.B.pgls.summary,Parameter == 'abs(SSD_wing)')
HPD_Interval_B_W <- HPDinterval(as.mcmc(Subset.B.pgls.summary$Estimate), prob=0.95) %>% as.data.frame %>% dplyr::mutate(Parameter = 'abs(SSD_wing)')

Subset.B.plot2 <-Subset.B.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-2.5, 4)) +
  xlab("Estimate (sexual size dimorphism)") + ylab("") +
  geom_errorbarh(data = HPD_Interval_B_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.DR.pgls.summary <- dr.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|Intercept")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% Polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% Polygny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% Polygny", 
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.DR.pgls.summary$Parameter <- factor(Subset.DR.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% Polygyny", "5-20% Polygny", ">20% Polygny"))

#Get HPD estimates
HPD_DR_Mating <- Subset.DR.pgls.summary %>%
  dplyr::group_by(Parameter) %>%
  summarise(lower = HPDinterval(as.mcmc(Estimate), prob=0.95)[1],
            upper = HPDinterval(as.mcmc(Estimate), prob=0.95)[2])

Subset.DR.Mating.Plot <-Subset.DR.pgls.summary %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)") %>%
  ggplot(aes(x = Estimate, y = Test, fill = Parameter, colour = Parameter)) +
  geom_density(aes(y = ..scaled..),
               alpha = 0.4,
               position = position_nudge(y= 1), colour="black")+
  #geom_jitter(shape = 21, alpha = 0.5, size = 1, fill="black", position = position_nudge(y= 0.4))+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-0.3, 0.3)) +
  xlab("") + ylab("") +
  geom_errorbarh(data = HPD_DR_Mating %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)"), 
  aes(y = Test, 
      xmin = lower, 
      xmax = upper, 
      colour = Parameter), 
  inherit.aes = F, height = 0, position = position_nudge(y = c(-0.1,-0.25, -0.4)), size = 1) +
  geom_text(data = HPD_DR_Mating %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)"), 
  aes(y = Test, 
      x = lower, 
      colour = Parameter, 
      label = Parameter), 
  inherit.aes = F, height = 0,
  position = position_nudge(y = c(-0.1,-0.25, -0.4), x = -0.095), size = 3.25) +
  scale_fill_manual(values = brewer.pal(8, "Greens")[6:8]) +
  scale_color_manual(values = brewer.pal(8, "Greens")[6:8])

#### ND ####

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.ND.pgls.summary <- nd.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|Intercept")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% Polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% Polygny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% Polygny",
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.ND.pgls.summary$Parameter <- factor(Subset.ND.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% Polygyny", "5-20% Polygny", ">20% Polygny"))

#Get HPD estimates
HPD_ND_Mating <- Subset.ND.pgls.summary %>%
  dplyr::group_by(Parameter) %>%
  summarise(lower = HPDinterval(as.mcmc(Estimate), prob=0.95)[1],
            upper = HPDinterval(as.mcmc(Estimate), prob=0.95)[2])

Subset.ND.Mating.Plot <-Subset.ND.pgls.summary %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)") %>%
  ggplot(aes(x = Estimate, y = Test, fill = Parameter, colour = Parameter)) +
  geom_density(aes(y = ..scaled..),
               alpha = 0.4,
               position = position_nudge(y= 1), colour="black")+
  #geom_jitter(shape = 21, alpha = 0.5, size = 1, fill="black", position = position_nudge(y= 0.4))+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-0.3, 0.3)) +
  xlab("") + ylab("") +
  geom_errorbarh(data = HPD_ND_Mating %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)"), 
  aes(y = Test, 
      xmin = lower, 
      xmax = upper, 
      colour = Parameter), 
  inherit.aes = F, height = 0, position = position_nudge(y = c(-0.1,-0.25, -0.4)), size = 1) +
  geom_text(data = HPD_ND_Mating %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)"), 
  aes(y = Test, 
      x = lower, 
      colour = Parameter, 
      label = Parameter), 
  inherit.aes = F, height = 0,
  position = position_nudge(y = c(-0.1,-0.25, -0.4), x = -0.095), size = 3.25) +
  scale_fill_manual(values = brewer.pal(8, "Greens")[6:8]) +
  scale_color_manual(values = brewer.pal(8, "Greens")[6:8])

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.B.pgls.summary <- b.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|(Intercept)")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% Polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% Polygny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% Polygny", 
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.B.pgls.summary$Parameter <- factor(Subset.B.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% Polygyny", "5-20% Polygny", ">20% Polygny"))

#Get HPD estimates
HPD_B_Mating <- Subset.B.pgls.summary %>%
  dplyr::group_by(Parameter) %>%
  summarise(lower = HPDinterval(as.mcmc(Estimate), prob=0.95)[1],
            upper = HPDinterval(as.mcmc(Estimate), prob=0.95)[2])

Subset.b.mating.Plot <-Subset.B.pgls.summary %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)") %>%
  ggplot(aes(x = Estimate, y = Test, fill = Parameter, colour = Parameter)) +
  geom_density(aes(y = ..scaled..),
               alpha = 0.4,
               position = position_nudge(y= 1), colour="black")+
  #geom_jitter(shape = 21, alpha = 0.5, size = 1, fill="black", position = position_nudge(y= 0.4))+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-0.3, 0.3)) +
  xlab("Estimate (Mating System vs Monogamy)") + ylab("") +
  geom_errorbarh(data = HPD_B_Mating %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)"), 
  aes(y = Test, 
      xmin = lower, 
      xmax = upper, 
      colour = Parameter), 
  inherit.aes = F, height = 0, position = position_nudge(y = c(-0.1,-0.25, -0.4)), size = 1) +
  geom_text(data = HPD_B_Mating %>% 
  filter(Parameter != "(Intercept)") %>% 
  mutate(Test = "Mating System (vs Monogamy)"), 
  aes(y = Test, 
      x = lower, 
      colour = Parameter, 
      label = Parameter), 
  inherit.aes = F, height = 0,
  position = position_nudge(y = c(-0.1,-0.25, -0.4), x = -0.095), size = 3.25) +
  scale_fill_manual(values = brewer.pal(8, "Greens")[6:8]) +
  scale_color_manual(values = brewer.pal(8, "Greens")[6:8])

ggarrange(Subset.ND.plot,Subset.ND.plot2,Subset.ND.Mating.Plot,
          Subset.DR.plot,Subset.DR.plot2,Subset.DR.Mating.Plot,
          Subset.B.plot,Subset.B.plot2,Subset.b.mating.Plot, ncol=3)
```

<!-- **Figure S18:** Estimates of the effect of individual sexual selection components included in the PPCA (paternal care and wing size dimorphism) on three measures of speciation rate ($\lambda_{DR}$, $\lambda_{ND}$ and $\lambda_{BAMM}$). Estimates are presented as density intervals from pgls models on 300 phylogentic trees.   -->
